---
name: Savannah L.
surname: Miller
position: "PhD Candidate, Epidemiology & Biostatistics"
address: "University of Georgia College of Public Health"
phone: 423 544 2453 
email: 'savannah.hammerton@uga.edu'
github: slmillerepi
linkedin: slmillerepi
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(googledrive)
library(readxl)
library(tibble)
library(tidyverse)
# googledrive::drive_download('cv_dat2',
#                             path = here::here("cv_dat2.xlsx"),
#                             overwrite = TRUE)
cv_data <- readxl::read_xlsx(here::here('cv_dat2.xlsx'))

options(tinytex.verbose = TRUE)
```

# About

Graduate student pursuing a PhD in Epidemiology and Biostatistics, with a concentration in Data Analysis and Modeling. I have a keen interest in infectious diseases, focusing on the correlates of protection for viral vaccine development and evaluation. My background in healthcare has equipped me with a robust understanding of disease determinants, prevention strategies, treatment options, and health outcomes, providing valuable insights into the real-world implications of public health research and practice on individuals. I am passionate about leveraging my skills and knowledge to build a career dedicated to improving public health and benefiting communities.

# Education

```{r education}
cv_data |> 
  filter(section == 'education', in_resume == 'TRUE') |> 
  detailed_entries(
    title,
    paste0(as.character(as.integer(start)), '-', if_else(end == "Present", as.character(end), sprintf("%i", as.integer(end)))),
    institution, 
    loc
  )
```



# Relevant Experience 

```{r experience}
cv_data |> 
  filter(section == 'rel_exp', in_resume == 'TRUE') |> 
  detailed_entries(
    title,
    paste0(as.character(as.integer(start)), '-', if_else(end == "Present", as.character(end), sprintf("%i", as.integer(end)))),
    institution, 
    loc,
    description
  )
```

# Research

```{r}
cv_data |> 
  filter(section == 'projects', in_resume == 'TRUE') |> 
  detailed_entries(
    description, 
    paste0(as.character(as.integer(start)), '-', if_else(end == "Present", as.character(end), sprintf("%i", as.integer(end)))),
    title,
    institution
  )

```


# Presentations

```{r presentations}
cv_data |> 
  filter(section == "presentations", in_resume == "TRUE") |> 
  detailed_entries(
    institution, 
    paste0(as.integer(start)),
    title, 
    loc,
    description
  )
```

# Publications

  - Note: Name change from Savannah M. Hammerton to Savannah L. Miller occurred in 2025.

**Hammerton, S. M.**, Billings, W. Z., Hemme, H., Ross, T. M., Shen, Y., & Handel, A. (2024). Estimating Standard-Dose and High-Dose Fluzone Vaccine Efficacies for Influenza A Based on Hemagglutination Inhibition Titers. The Journal of Infectious Diseases, jiae615. https://doi.org/10.1093/infdis/jiae615

Billings, W. Z., Ge, Y., Knight, J. H., Hemme, H., **Hammerton, S. M.**, Skarlupka, A. L., Cao, W., Shen, Y., Bahl, J., Thomas, P. G., Ross, T. M., & Handel, A. (2025). High-Dose Inactivated Influenza Vaccine Inconsistently Improves Heterologous Antibody Responses in an Older Human Cohort. The Journal of Infectious Diseases, jiaf003. https://doi.org/10.1093/infdis/jiaf003


# Teaching and Mentorship 

```{r mentorship}
cv_data |> 
  filter(section == 'mentorship', in_resume == 'TRUE') |>
  detailed_entries(
    institution,
    paste0(as.character(as.integer(start)), '-', if_else(end == "Present", as.character(end), sprintf("%i", as.integer(end)))),
    title,
    loc,
    description
  )
```

# Honors and Awards

```{r honors_awards}
cv_data |> 
  filter(section == 'honors_awards', in_resume == 'TRUE') |>
  detailed_entries(
    institution,
    paste0(as.character(as.integer(start)), '-', if_else(end == "Present", as.character(end), sprintf("%i", as.integer(end)))),
    title,
    loc,
    description
  )
```


# Certifications and Professional Training

```{r certifications}
cv_data |> 
  filter(section == 'certs', in_resume == 'TRUE') |>
  detailed_entries(
    loc,
    as.character(as.integer(end)), 
    title
  )
```


# Service 

```{r service}
cv_data |> 
  filter(section == "service", in_resume == "TRUE") |> 
  detailed_entries(
    title,
    paste0(as.character(start)),
    institution,
    loc,
    description
  )
```

# Organizations

```{r org}
cv_data |>
  filter(section == 'org', in_resume == 'TRUE') |>
  detailed_entries(
    NA,
    paste0(as.character(as.integer(start)), '-', if_else(end == "Present", as.character(end), sprintf("%i", as.integer(end)))),
    institution,
    loc
  )
```


# Skills

```{r skills}
cv_data |> 
  filter(section == 'skills', in_resume == 'TRUE') |> 
  detailed_entries(
    description,
    NA,
    title
  )
```






