---
name: Savannah
surname: Hammerton
position: "PhD Student, Epidemiology & Biostatistics"
address: "University of Georgia College of Public Health"
phone: 423 544 2453 
email: 'savannah.hammerton@uga.edu'
github: smhammerton
linkedin: smhammerton
www: smhammerton.com
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(googledrive)
library(readxl)
library(tibble)
library(tidyverse)
# googledrive::drive_download('cv_dat2',
#                             path = here::here("cv_dat2.xlsx"),
#                             overwrite = TRUE)
cv_data <- readxl::read_xlsx(here::here('cv_dat2.xlsx'))

options(tinytex.verbose = TRUE)
```

# About

Graduate student working towards PhD in Epidemiology & Biostatistics (concentration in Data Analysis and Modeling). Particular interest and research emphasis in infectious diseases, correlates of protection for viral vaccine development, infectious disease dynamics, and modeling. Past experience in healthcare, providing strong contextual understanding of disease determinants, prevention, treatment, and outcomes, as well as an understanding of the real world implications of public health research and practice on individuals. This experience also drives context-aware data analytic approaches to answering epidemiological questions. Passionate and driven to build a career that benefits others. 

# Education

```{r education}
cv_data |> 
  filter(section == 'education', in_resume == 'TRUE') |> 
  detailed_entries(
    title,
    paste0(as.character(as.integer(start)), '-', if_else(end == "Present", as.character(end), sprintf("%i", as.integer(end)))),
    institution, 
    loc
  )
```



# Relevant Experience 

```{r experience}
cv_data |> 
  filter(section == 'rel_exp', in_resume == 'TRUE') |> 
  detailed_entries(
    title,
    paste0(as.character(as.integer(start)), '-', if_else(end == "Present", as.character(end), sprintf("%i", as.integer(end)))),
    institution, 
    loc,
    description
  )
```

# Research

```{r}
cv_data |> 
  filter(section == 'projects', in_resume == 'TRUE') |> 
  detailed_entries(
    description, 
    paste0(as.character(as.integer(start)), '-', if_else(end == "Present", as.character(end), sprintf("%i", as.integer(end)))),
    title,
    institution
  )

```


# Presentations

```{r presentations}
cv_data |> 
  filter(section == "presentations", in_resume == "TRUE") |> 
  detailed_entries(
    institution, 
    paste0(as.integer(start)),
    title, 
    loc,
    description
  )
```


# Honors and Awards

```{r honors_awards}
cv_data |> 
  filter(section == 'honors_awards', in_resume == 'TRUE') |>
  detailed_entries(
    institution,
    as.character(as.integer(end)),
    title,
    loc
  )
```

# Certifications and Professional Training

```{r certifications}
cv_data |> 
  filter(section == 'certs', in_resume == 'TRUE') |>
  detailed_entries(
    loc,
    as.character(as.integer(end)), 
    title
  )
```

\pagebreak

# Service 

```{r service}
cv_data |> 
  filter(section == "service", in_resume == "TRUE") |> 
  detailed_entries(
    title,
    paste0(as.character(start)),
    institution,
    loc,
    description
  )
```


# Skills

```{r skills}
cv_data |> 
  filter(section == 'skills', in_resume == 'TRUE') |> 
  detailed_entries(
    description,
    NA,
    title
  )
```

# Organizations 

```{r organizations}
cv_data |> 
  filter(section == 'org', in_resume == 'TRUE') |> 
  detailed_entries(
    description, 
    paste0(as.character(as.integer(start)), '-', if_else(end == "Present", as.character(end), sprintf("%i", as.integer(end)))),
    institution,
    loc
  )
```




